---
title: "Project EDA"
author: "Christina Rhees"
date: "10/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(corrplot)
library(GGally)
cleaned = readRDS("cleaned.RData")
```

Checking for collinearity between variables and the relationship between continuous variables.
```{r}
# collinearity check
cont_vals = c(3, 5:12, 17:18, 22)
cleaned_cor = cor(cleaned[, cont_vals], use="complete.obs")
corrplot::corrplot(cleaned_cor)

# option to plot scatter of X number of columns
plot(cleaned[, cont_vals[c(2:9,12)]])
```

Looking at players efficiency over the seasons to see if the general values have changed over time - this will indicate if season has any effect on any Player Evaluation Metrics.

There appears to be no change over seasons.
```{r}
ggplot(data = cleaned, mapping = aes(x = Season, y = WS)) +
  geom_point() + geom_smooth(method='lm', formula= y~x)

ggplot(data = cleaned, mapping = aes(x = Season, y = VORP)) +
  geom_point() + geom_smooth(method='lm', formula= y~x)

ggplot(data = cleaned, mapping = aes(x = Season, y = BPM)) +
  geom_point() + geom_smooth(method='lm', formula= y~x)

ggplot(data = cleaned, mapping = aes(x = Season, y = PER)) +
  geom_point() + geom_smooth(method='lm', formula= y~x)

```

Checking for interaction: 

There doesn't appear to be a huge difference between each position besides when looking at WS, I will check later with the models.
```{r}
ggplot(data = na.omit(cleaned), mapping = aes(x = ExactAge, y = WS, color = Pos.x)) +
  geom_point() +
  xlab("Exact Age") +
  ylab("Win Shares") + 
  labs(color = "Position") +
  geom_smooth()

ggplot(data = na.omit(cleaned), mapping = aes(x = ExactAge, y = VORP, color = Pos.x)) +
  geom_point() +
  xlab("Exact Age") +
  ylab("VORP") + 
  labs(color = "Position") +
  geom_smooth()

ggplot(data = cleaned, mapping = aes(x = ExactAge, y = BPM, color = Pos.x)) +
  geom_point() +
  geom_smooth()

```
```{r}
ggplot(data = cleaned, mapping = aes(x = ExactAge, y = WS/48)) +
  geom_point() +
  geom_smooth()
```

```{r}
ggplot(data = na.omit(cleaned), mapping = aes(x = Pos.x, y = WS)) + geom_boxplot()
```

